Pyg4ometry: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-04-11 public/paper/pyg4ometry.tex
Updated notes in paper

\subsection{TODO}
\begin{itemize}
\item disjoint subtractions?
\item quadric specialisation
\item second order lattice
\item Materials 
\end{itemize}
\section{Geant4 to FLUKA conversion}
It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 solids can be mapped to a FLUKA CSG region.
Some solids in Geant4 directly map to a FLUKA body, others need a construction of a simple FLUKA CSG tree. Table~\ref{tab:geant2fluka}
lists the mapping between geant4 solids and the bodies used to compose a fluka region.

@@

\section{CAD to Geant4 conversion }
STEP and IGES files can be loaded into pyg4ometry, via an interface based on FreeCAD. FreeCAD is an open source CAD/CAM program, which in turn 
is based on OpenCASCADE. A STEP CAD file could be considered as a hierarchical tree of {\it part assemblies} and {\it part features}, where a part assembly is a 
collection of part features. A part feature can be used to create  a triangular mesh which can used to create a pyg4ometry tessellated solid. Assignment of materials 
and visualisation attributes.

@@

\subsection{Editing existing models}
Often existing CAD models have either missing details or too many details. Examples of too potentially superfluous detail are gaskets and bolts

>>>>

\subsection{TODO}
\begin{itemize}
\item disjoint subtractions?
\item quadric specialisation
\item second order lattice
\item Materials 
\end{itemize}
\section{GDML to FLUKA conversion}
It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 solids can be mapped to a FLUKA CSG region.
Some solids in Geant4 directly map to a FLUKA body, others need a construction of a simple FLUKA CSG tree. Table~\ref{tab:geant2fluka}
lists the mapping between geant4 solids and the bodies used to compose a fluka region.

@@

\section{CAD to GDML conversion }
STEP and IGES files can be loaded into pyg4ometry, via an interface based on FreeCAD. FreeCAD is an open source CAD/CAM program, which in turn 
is based on OpenCASCADE. A STEP CAD file could be considered as a hierarchical tree of {\it part assemblies} and {\it part features}, where a part assembly is a 
collection of part features. A part feature can be used to create  a triangular mesh which can used to create a pyg4ometry tessellated solid. Assignment of materials 
and visualisation attributes.

@@

\subsection{Modifying existing models}
Often existing CAD models have either missing details or too many details. Examples of too potentially superfluous detail are gaskets and bolts
